Experience-Biased Symbolic Planning

### 2014-05-14 AAAI_AuthorKit/paper.tex
ALL EXPERIMENTS

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Maxim Likhachev, Sven Koenig)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar \and Mike Phillips \and Maxim Likhachev\\
Carnegie Mellon University\\
5000 Forbes Ave,\\
Pittsburgh, PA 15213\\
\And Sven Koenig\\
University of Southern California\\
Los Angeles, CA 90089
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP2 by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

@@

\includegraphics[scale=0.4]{Pentagon.png}

@@

\section{Experimental Setup}

@@

\section{Experimental Results}

\includegraphics[scale=0.4]{AIPlot.png}

@@

\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    Domain & 0 steps & 10 steps & 20 steps
    \\ \hline
    BlocksWord & 0 & 0 & 0
    \\ \hline
    Grid & 0 & 0 & 0
    \\ \hline
    Satellite & 0 & 0 & 0
    \\ \hline
    \end{tabular}
\end{center}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
% AAAI format packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
% Additional packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
% END Additional packages
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Experience-Biased Symbolic Planning)
/Author (Aram Ebtekar, Mike Phillips, Sven Koenig, Maxim Likhachev)
/Keywords (symbolic planning, E-graph, experience-biasedh, A* search, STRIPS, HSP)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Experience-Biased Symbolic Planning}
\author{Aram Ebtekar$^\dagger$ \and Mike Phillips$^\dagger$ \and Sven Koenig\thanks{University of Southern California, Los Angeles, CA} \and Maxim Likhachev% <-this % stops a space
\thanks{Carnegie Mellon University, Pittsburgh, PA.
We thank Willow Garage for their support of this work. This research was also sponsored by ARL, under the Robotics CTA program grant W911NF-10-2-0016.}% <-this % stops a space
%
}
\maketitle
\begin{abstract}
\begin{quote}
Weighted A* search is the foundation for state-of-the-art domain-independent symbolic planners.
An important open challenge for these planners is to utilize experience with similar planning problems to speed up subsequent planning episodes.
Experience graphs have recently shown promise as a technique for plan reuse in the context of weighted A* searches in robotics, by biasing them towards a subgraph of the search space, typically chosen to consist of the edges used in previous plans.
In this paper, we demonstrate how to augment symbolic planners with
experience graphs, using the HSP2 planner as a representative
example.
The resulting planners are able to trade off seamlessly
between plan quality and runtime and thus have advantages over past
plan-reuse techniques, such as planning by analogy.
We demonstrate
experimentally that our planner speeds up HSP2 by a factor of 2 or more on
many domains while achieving about the same plan quality.
\end{quote}
\end{abstract}

@@

Classically, case-based reasoning methods 
such as PRIAR~\cite{Kamb:92}, SPA~\cite{Hank:95}, MRL~\cite{Koeh:94}, and NoLimit~\cite{mljournal}
have been used recall 
previous plans that appear similar to the current problem and 
then adapt them to meet the new specifications.
Compared to these methods, our work reuses prior experience in
the context of modern weighted A* methods. We also provide
a bound on the suboptimality of the solution.

Recently there has been work on incorporating prior knowledge 
into modern planners (based on weighted A* and powerful heuristics).
For instance, GPG~\cite{Gere:00} uses planning graphs to adapt a prior path to the 
new scenario by searching locally within windows around plan 
inconsistencies. To guarantee completeness, the windows can grow 
if solutions are not found until they contrain the whole plan.
In this work~\cite{DBLP:conf/iccbr/RosaOB07} case-based reasoning is used to choose the 
order of state evaluations of EHC (enforced hill-climbing) which 
is a component in modern planners such as FF.

OAKplan~\cite{Serina:2010:KFC:1860143.1860472} is a recent 
case-based reasoning method which converts 
planning instances to into a compact graph representation and 
then uses recent kernel methods for matching labeled graphs to select
a similar case to the problem at hand. The selected case is then 
adapted using LPG-ADAPT~\cite{Fox06planstability} LPG-ADAPT is a replanning method 
encourages \textit{plan stability}, which tries to make 
sure that the new plan is as similar to the previous plan as possible. 
The method also uses a modern heuristic search approach.

ERRT-PLAN~\cite{workshop-icaps12-errtplan} presents a very different 
approach to reuse in planning. 
Similar to E-Graphs, ERRT has its roots in motion planning~\cite{Bruce:2002}.
ERRT-PLAN applies this sampling-based motion planner that leverages 
reuse to symbolic planning. The planner randomly chooses to extend 
the search tree toward the goal, toward goals from previous 
plans, or to reuse an action from a previous plan. 
The extension operations are based on modern heuristic search
planners.
The stochastic nature of the direction the search progresses toward
allows it to overcome local minima caused by misleading heuristics.

The primary difference between our approach and previous ones 
is that we plan with prior experience in a way that have provable
bounds on suboptimality of the solution. The use of E-Graphs also
allows us to formulate this in a way that the user has control over
this suboptimality bound with an intuitive parameter that trades
reuse (speed) for solution quality.

\section{Old version of related works (to delete)}

@@

\begin{center}
\includegraphics[scale=0.5]{Pentagon.png}
\end{center}

@@

\section{Experiment 1}

@@

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_20_0.png}
	\end{center}
	\caption{20\% E-graph}
	 \label{fig:s_20_0}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_50_0.png}
	\end{center}
	\caption{50\% E-graph}
	 \label{fig:s_50_0}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_80_0.png}
	\end{center}
	\caption{80\% E-graph}
	 \label{fig:s_80_0}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_20_0.png}
	\end{center}
	\caption{20\% E-graph}
	 \label{fig:c_20_0}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_50_0.png}
	\end{center}
	\caption{50\% E-graph}
	 \label{fig:c_50_0}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_80_0.png}
	\end{center}
	\caption{80\% E-graph}
	 \label{fig:c_80_0}
\end{figure}

\begin{table}
	\begin{center}
	    \begin{tabular}{| l | l | l | l | l |}
	    \hline
	    Domain & Inst & 20\% & 50\% & 80\%
	    \\ \hline
	    blocksworld & 35 & 1.08-1.82 & 1.37-3.73 & 1.90-5.84
	    \\ \hline
	    driverlog & 14 & 1.00-1.49 & 1.11-1.58 & 1.15-1.60
	    \\ \hline
	    elevators & 30 & 1.00-1.62 & 1.00-2.84 & 1.04-3.19
	    \\ \hline
	    freecell & 34 & 1.00-1.06 & 1.00-1.12 & 1.00-1.08
	    \\ \hline
	    grid & 2 & 1.07-1.18 & 2.16-3.57 & 2.22-3.75
	    \\ \hline
	    logistics00 & 28 & 0.91-1.04 & 0.98-1.13 & 1.03-1.19
	    \\ \hline
	    logistics98 & 5 & 0.95-1.01 & 1.09-1.62 & 1.24-3.00
	    \\ \hline
	    mprime & 19 & 1.00-1.00 & 1.00-1.07 & 1.00-2.46
	    \\ \hline
	    pegsolitaire & 29 & 1.00-3.57 & 1.13-4.49 & 1.68-6.63
	    \\ \hline
	    pipesworld-notankage & 15 & 1.00-3.27 & 1.00-7.07 & 1.00-9.95
	    \\ \hline
	    pipesworld-tankage & 8 & 1.00-1.00 & 1.00-1.02 & 1.00-1.45
	    \\ \hline
	    rovers & 13 & 0.97-1.23 & 1.23-7.09 & 1.23-7.17
	    \\ \hline
	    satellite & 16 & 0.99-1.00 & 1.00-1.26 & 1.00-1.26
	    \\ \hline
	    scananalyzer & 16 & 1.00-1.15 & 0.93-1.20 & 1.00-1.36
	    \\ \hline
	    sokoban & 11 & 1.12-2.10 & 1.32-3.02 & 1.56-7.80
	    \\ \hline
	    tpp & 10 & 1.00-1.00 & 1.00-1.23 & 1.00-2.31
	    \\ \hline
	    transport & 23 & 1.00-1.14 & 1.09-1.86 & 1.19-1.89
	    \\ \hline
	    zenotravel & 13 & 1.02-1.15 & 1.08-1.44 & 1.14-1.58
	    \\ \hline
	    TOTAL & 321 & 1.00-1.29 & 1.00-1.91 & 1.02-2.68
	    \\ \hline
	    \end{tabular}
	\end{center}
	\caption{Speedups for various E-graph \%s over various domains.}
	 \label{tab:percent}
\end{table}

\section{Experiment 2}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_100_5.png}
	\end{center}
	\caption{5 random steps}
	 \label{fig:s_100_5}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_100_20.png}
	\end{center}
	\caption{20 random steps}
	 \label{fig:s_100_20}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Speedup_100_50.png}
	\end{center}
	\caption{50 random steps}
	 \label{fig:s_100_50}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_100_5.png}
	\end{center}
	\caption{5 random steps}
	 \label{fig:c_100_5}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_100_20.png}
	\end{center}
	\caption{20 random steps}
	 \label{fig:c_100_20}
\end{figure}

\begin{figure}
	\begin{center}
	\includegraphics[scale=0.5]{Cost_100_50.png}
	\end{center}
	\caption{50 random steps}
	 \label{fig:c_100_50}
\end{figure}

@@

\begin{table}
	\begin{center}
	    \begin{tabular}{| l | l | l | l | l |}
	    \hline
	    Domain & Inst & 5 steps & 20 steps & 50 steps
	    \\ \hline
	    blocksworld & 35 & 2.12-7.92 & 2.12-8.70 & 2.21-6.25
	    \\ \hline
	    driverlog & 14 & 0.86-2.42 & 0.85-1.30 & 0.82-1.20
	    \\ \hline
	    elevators & 30 & 1.09-4.04 & 0.99-2.76 & 0.90-2.06
	    \\ \hline
	    grid & 2 & 2.21-3.71 & 1.11-1.34 & 1.10-1.30
	    \\ \hline
	    logistics00 & 28 & 1.00-1.15 & 0.90-1.11 & 0.84-1.18
	    \\ \hline
	    logistics98 & 5 & 1.01-2.95 & 0.82-2.06 & 0.80-2.41
	    \\ \hline
	    pipesworld-notankage & 15 & 1.09-5.30 & 1.00-5.46 & 1.00-2.88
	    \\ \hline
	    pipesworld-tankage & 8 & 1.00-1.20 & 0.99-1.00 & 1.00-1.13
	    \\ \hline
	    rovers & 13 & 1.00-1.50 & 1.00-1.00 & 1.00-1.00
	    \\ \hline
	    satellite & 16 & 0.91-1.25 & 0.87-1.15 & 0.90-1.43
	    \\ \hline
	    scananalyzer & 16 & 0.74-1.52 & 1.00-1.00 & 1.00-1.00
	    \\ \hline
	    transport & 23 & 1.26-1.91 & 0.93-1.87 & 0.98-1.46
	    \\ \hline
	    zenotravel & 13 & 0.80-1.27 & 0.84-1.02 & 1.00-1.00
	    \\ \hline
	    TOTAL & 218 & 0.99-2.72 & 1.00-2.07 & 1.00-1.88
	    \\ \hline
	    \end{tabular}
	\end{center}
	\caption{Speedups for various random walk distances over different domains.}
	 \label{tab:walk}
\end{table}
